Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach

### 2024-11-03 paper/paper.qmd
update paper

---
title: "Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach"
subtitle: "Kamala Harris expects to win on 47.5%, leads Donald Trump by about 1% in 2024 US election"
author: 
  - Diana Shen
  - Jinyan Wei
  - Jerry Yu
thanks: "Code and data are available at: [https://github.com/DianaShen1224/Forecast-2024-US-election](https://github.com/DianaShen1224/Forecast-2024-US-election)."
date: today
date-format: long
abstract: "This study models the 2024 U.S. Presidential Election by analyzing polling data with adjustments for factors like recency and sample size, simulating an approach that captures up-to-date voter sentiment. Using recent 4 months aggregated poll data, the model identifies shifts in candidate support across key battleground states, providing a nuanced view of evolving preferences as election day approaches. By emphasizing recent, high-quality polls, the analysis improves predictive reliability, offering insights that could inform campaign strategies and public discourse. These findings highlight the value of weighting and time-sensitive adjustments in forecasting methods, balancing accuracy with responsiveness to the latest trends."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

Understanding voter sentiment is essential for both political campaigns
and analysts, especially with the upcoming U.S. election on the horizon.
Public opinion is highly dynamic and can change swiftly due to various
influences, including media coverage, campaign tactics, and major
events. This study aims to forecast the percentage of support for Kamala
Harris, offering insights into the elements that shape voter preferences
as the election nears. By examining data from multiple polling sources,
we intend to pinpoint the key factors influencing support, such as the
poll's end date, the polling organization, geographic location, and the
poll's score.

Research by @GelKin93 underscores that while polls can
exhibit variability over a campaign period, they can provide reliable
predictions when adjusted for temporal changes and fundamental factors.
Additionally, @politic highlight the importance of
timing in polling, showing that data closer to election day tends to
stabilize and therefore becomes more predictive. Our research seeks to
fill a gap in existing literature that often fails to address the
complexities of polling data, thereby enhancing our understanding of
voter behavior within the electoral context.

@@

Our findings reveal a notable positive correlation between the end date
and the percentage of support, indicating that as the election
approaches, voter support tends to increase. We also observed
considerable variability in support levels based on the polling
organization and state, with certain pollsters consistently reporting
higher support for Harris. The quality of the polls significantly
affected results, with more reputable polls correlating with higher
levels of support. These insights emphasize the necessity of considering
both the timing of polls and the characteristics of different polling
firms when analyzing public opinion.

This research is important because precise predictions of voter support
are crucial for effective campaign strategies. By identifying the main
factors influencing support for Harris, campaign teams can customize
their outreach and messaging to resonate better with voters.
Furthermore, recognizing the differences across various polling
organizations and states can assist in resource allocation and strategic
focus during the campaign. Given that elections can be decided by narrow
margins, having trustworthy insights into voter preferences can
substantially influence the final outcomes.

The structure of this paper is organized as follows: @sec-data 
provides details on the data sources and variables used in our analysis.
@sec-model explains the modeling approach, including the assumptions
and specifications of our linear regression framework. In
@sec-result, we present our findings, emphasizing the key predictors
of Harris's support. Finally, @sec-discussion explores the
implications of our results and suggests potential directions for future
research. @sec-a provide external data detail, @sec-b provide
model detail, @sec-c provide a exploration for pollster Siena College's
methodology, and  @sec-d provide a idealized methodology for polling the poll.

@@

In this study, we utilized several R packages to enhance our data
manipulation, modeling, and visualization capabilities. The tidyverse
package offered a comprehensive set of tools for data wrangling and
analysis, improving workflow efficiency [@thereferencecanbewhatever].
The here package aided in managing file paths, allowing for easy access
to our data files [@citehere]. We relied on janitor to perform data
cleaning, as it provides functionalities to identify and rectify quality
issues within the dataset [@citejanitor]. For handling date-related
operations, the lubridate package proved invaluable, simplifying the
manipulation of time variables [@citelubridate]. Arrow supported
efficient data input and output in a performance-oriented format,
essential for managing larger datasets [@citearrow]. We use ggplot2 [@citeggplot2] to visualize the analysis of data. In addition to the core packages, we employed several specialized libraries to facilitate specific analytical tasks. The modelsummary package enabled us to generate clean, interpretable model summaries, streamlining the reporting of regression and other statistical results [@citemodelsummary]. RColorBrewer provided color palettes for visualizations, enhancing clarity and visual appeal in our plots [@citeRColorBrewer]. The future package supported parallel processing, optimizing the runtime of intensive computations, especially beneficial in model training [@citefuture]. Finally,for resampling and bootstrapping techniques, we utilized the boot package, which allowed us to assess model stability and reliability [@citeboot1;@citeboot2]. caret facilitated model training and validation, offering a unified interface for cross-validation and performance metrics [@citecaret]. Our coding practices and file organization were informed by the structure outlined
in @tellingstories.

@@

After gathering the responses, the data is subjected to thorough
cleaning and validation procedures to rectify inconsistencies and handle
any missing information. This step is crucial for ensuring that the
dataset accurately mirrors the electorate's sentiments. Following data
cleaning, polling results are aggregated to smooth out individual poll
biases and mitigate random error. This aggregation process leverages
weighting based on poll quality, sample size, recency, and the
historical accuracy of each polling agency, as seen in FiveThirtyEight’s
approach (Silver, 2018; Jackman, 2005). By combining multiple polls, the
aggregation method produces a more reliable picture of public opinion
trends over time.

Each entry in the finalized dataset reflects an individual's viewpoint
at a given moment, enabling a detailed analysis of the factors that
shape public opinion as the election nears. This structured methodology
effectively converts subjective opinions into measurable data, providing
valuable insights into voter behavior and preferences.

@@

The end date is the final day of data collection for a poll, indicating
when the survey period concluded. This date provides crucial context for
the poll results, as public opinion may change over time in response to
events, campaign actions, or other influencing factors. In our analysis, we only choose the polls with end date after July 21 2024, which Kamala Harris first declared in the election.

@@

Recency is a newly created predictor variable in our dataset, specifically
for use in our model. It is calculated as follows Recency = Election Date - End Date,
where Election Date is set to November 5th. This variable quantifies the time
interval between the poll's end date and the election date as a measure of the poll's
relevance and potential impact on voter behavior. In general, polls conducted closer
to the election date provide a more accurate picture of public opinion. The original
dataset includes only dates, and by mutating this variable, we can more intuitively
interpret the number of days before the election that each data point was collected.
Converting this to discrete data enhances its usefulness in constructing predictive models.
@fig-recency reveals a strong focus on recent polling data, with the highest frequency of polls occurring within the first few days and gradually declining as recency increases. Periodic peaks around 30, 60, and 90 days suggest some regularity in polling schedules, though the overall trend emphasizes newer data. This distribution highlights the prioritization of recent polls in the dataset.

@@

@fig-state displays the distribution of polls by state, showing how
frequently polling organizations conducted surveys across various U.S.
states and at the national level. The "National" category has the
highest number of polls, indicating a strong emphasis on capturing
overall U.S. sentiment. Certain states, such as Pennsylvania, Wisconsin,
North Carolina, Arizona, Georgia, and Michigan, also show higher polling
frequencies, likely because these are battleground states with the
potential to influence the election outcome significantly. Toward the
right side of the chart, states with minimal polling activity, including
South Carolina, Iowa, and Washington, appear less frequently, possibly
due to their historically predictable or less competitive nature. This
distribution reflects the strategic focus of polling efforts, with
organizations prioritizing both national sentiment and swing states
where public opinion is more volatile. Overall, the chart provides
insight into where polling resources are allocated as election day
nears, emphasizing areas that could sway the final result.

@@

@fig-pollstertime shows the trend of percentage support for Kamala
Harris over time, with data points and smoothed trend lines for each
pollster. The graph shows the trend of the percentage of respondents supporting
Harris from August through October. Each color corresponds to a specific polling organization, with
prominent pollsters such as Beacon/Shaw, Ipsos, Siena/NYT, Emerson,
Quinnipiac, and YouGov. The smoothed lines reveal subtle trends over
time, with some pollsters like Emerson and Beacon/Shaw showing a slight
upward trend, while others like Siena/NYT display a downward trend.
@fig-pollstertime highlights the variability in poll results across
different organizations, reflecting each pollster's methodology and
sample.

@@

In this analysis, we use predictors that capture both the methodological
quality and structural aspects of each poll. Specifically, we include
variables such as `national_poll`, which reflects national support
trends; `pollster`, which represents differences in methodology and
reliability across polling organizations; and `population`, which
accounts for demographic and regional characteristics associated with
each poll. Our combined weighting approach further integrates factors
like recency and sample size to ensure that more recent, larger-sample
polls have a greater impact on the model's predictions, providing a
balanced and comprehensive assessment of candidate support.

@@

Our model reveals a portrait of a nation deeply divided, with Harris
holding a narrow 49% edge over Trump’s 47% in national support. However,
as recent elections have shown, the national popular vote does not
always translate into an Electoral College victory. The U.S. electoral
system, which awards each state’s electoral votes to the candidate with
the majority of votes in that state, means that winning the popular vote
nationally might still leave Harris short of the presidency. This
structural quirk played a defining role in the 2016 election, where
Hillary Clinton’s popular vote win failed to deliver the electoral
majority, paving Trump’s path to the White House. Our findings
underscore this enduring tension: while Harris may have a slight
national advantage, the true battle will be fought state by state, in a
handful of battlegrounds that could flip the election either way.

In states like Nevada and North Carolina, our model highlights just how
close the race remains. North Carolina, for instance, shows both candidates
locked in a near tie around 47% support—a statistical dead heat that
brings the state’s significance into sharp relief. Neveda, meanwhile,
leans modestly toward Trump, a reflection of the unique demographic and
political nuances shaping each battleground. These state-level insights
illuminate a critical truth: while national polls offer a snapshot of
overall sentiment, they risk obscuring the specific, local dynamics that
will ultimately decide the outcome. The stakes are high; these are the
states that could swing, the margins that will be watched closely on
election night, as even slight changes in turnout or last-minute shifts
in opinion could tip the balance. improve the number based on the graph results

Ultimately, these findings highlight the intricate dance between popular
sentiment and the electoral mechanics of American democracy—a system where
every vote counts, but some states matter just a bit more than others.

@@

In our analysis and shown result, we find out that the use of a weighted model helps to reduce volatility in predicted support trends by assigning greater importance to polls that are both recent and based on larger sample sizes. This approach effectively smooths out abrupt fluctuations that might otherwise result from older or smaller polls, providing a more stable and coherent view of voter sentiment. hough our data filtered with recent polls after Harris's candidacy announcement, voter sentiment remains fluid, with ongoing debates and events likely to influence preferences. By emphasizing recent polls, the model is more responsive to the latest shifts in public opinion, which is especially relevant as election day approaches and voters’ preferences may crystallize. Larger-sample polls, often conducted by established pollsters like Siena/NYT or Emerson, are assumed to be more reliable, and their increased weight in the model further reduces the likelihood of erratic changes driven by smaller, less consistent polls. This decreased volatility allows the model to present a clearer picture of the general support trend for each candidate, reducing noise and highlighting true shifts in sentiment. However, this smoothing effect may also mask some of the localized or short-term dynamics captured by less frequent or smaller-sample polls, which could provide unique insights into specific voter groups or state-level shifts.

@@

Yet, as with all models, limitations persist. While our weighting
system, with its emphasis on recent data, aims to capture a timely
snapshot of voter sentiment, it may miss sudden changes sparked by
campaign events or unexpected shifts in public discourse. The
variability in our state projections—ranging from a low estimate of 363
electoral votes for Harris to a high of 471—reflects the inherent
uncertainty in polling-based models, particularly given the constraints
of our data sources. This wide range suggests that while data-driven
insights can illuminate trends, they cannot fully account for the
unpredictable nature of electoral outcomes. While the dataset provides
an overall approval rating for Harris, it lacks a breakdown by factors
such as age, gender, income, and education, which are critical to
understanding the preferences of different groups of voters. Without
them, our analysis may have overlooked significant changes in specific
groups that could affect overall trends.

@@

To enhance the predictive power of the model, historical voting data, economic
indicators and major news events can be used as background variables. By analyzing
the impact of similar factors on voter sentiment in past elections, we can gain
insight into patterns and trends that may apply to the current campaign. For
example, high-profile events have historically influenced voter opinion, and
understanding these influences can provide a more complete picture of the factors
that drive support for each candidate. Given the underlying conditions that influence
voter preferences over time, this additional context would allow the model to make
more informed predictions.

Another possible improvement is the addition of detailed demographic information, such as age,
gender, income level, and educational background, which would allow us to identify trends among
specific groups of voters and thus greatly enhance our analysis. Different demographics often
have unique responses to campaign issues and activities; for example, younger voters may
prioritize different issues compared to older voters, and income level and educational
attainment may influence political preferences in complex ways. By incorporating this level
of granularity, future analyses can provide deeper insights into voter behavior and help
develop more targeted campaign strategies.

@@

The cleaned datasets for both candidates are then saved as Parquet files
for efficient storage and access in further modeling and analysis. This
structured approach ensures that the data is accurate, complete, and
optimized for insightful statistical analysis.

@@

In this section, we examine the main components of Siena's polling
methodology, including the target population, sampling frame,
recruitment processes, and sampling strategies. Additionally, we discuss
how Siena addresses non-response and review the strengths and weaknesses
of its questionnaire design. By detailing these elements, this appendix
clarifies how Siena College ensures the reliability and validity of its
polling results, offering valuable insights into voter behavior and
election dynamics.

@@

Siena College Polling Institute is a prominent pollster known for its
comprehensive and methodologically rigorous surveys. It specializes in
political polling and is particularly recognized for its work in
understanding voter sentiment during elections. Established in 1980 at
Siena College in New York's Capital District, the institute carries out
both expert and public opinion polls. [@aboutsiena].

@@

The sampling frame is a comprehensive list of registered voters, which
includes demographic information for each voter. This enables the
pollsters to ensure an appropriate representation of voters across
various parties, races, and regions [@poll].

@@

Siena use phone poll to recruit sample. Telephone polling is a way to
gather public opinion by contacting individuals via landlines and mobile
phones, using live interviewers to improve data quality and capture
nuanced responses. Through random digit dialing or voter registration
databases, researchers achieve a representative sample across
demographics.

@@

Stratified sampling enhances sample representativeness by ensuring that
smaller subgroups are adequately included, allowing researchers to
allocate resources more efficiently and gain deeper insights into
specific groups. However, this method can lead to **higher costs** due
to the extensive data collection and analysis needed, especially when
sampling large regions. Stratified sampling also introduces **complexity
in data analysis**, requiring advanced techniques to accurately
interpret subgroup data and appropriate weighting for each stratum.
Additionally, poorly defined strata or imbalanced sampling can lead to
sampling bias. While stratified sampling provides strong representation
and analytical depth, it also brings challenges related to cost,
complexity, and potential bias if not executed with care.

@@

-   Social desirability bias typically stems from the desire of
    respondents to avoid embarrassment and project a favorable image to
    others, resulting in respondents not revealing their actual
    attitudes. The prevalence of this bias will depend on the topic,
    questions, respondent, mode of the survey, and the social context.
    For instance, in some circles, anti-immigrant views are not
    tolerated, and those who hold them may try to hide them. In other
    settings, people express such views more freely.

@@

The questionnaire is concise and straightforward, reducing respondent
fatigue and enhancing clarity, which is crucial for maintaining
engagement. By incorporating both closed- and open-ended questions, it
allows for both quantifiable data and rich qualitative insights. Clear
response categories help reduce moderacy bias, encouraging participants
to choose decisively rather than defaulting to neutral answers.
Additionally, varied question types help mitigate acquiescence bias by
encouraging honest responses and avoiding leading language.

@@

This appendix details the methodology and design for conducting a U.S.
presidential election forecast survey with a budget of $\$100,000$. The
objective is to generate an accurate and reliable prediction of the
election outcome while ensuring data quality through meticulous
sampling, recruitment, validation, and aggregation of results.\

@@

In the subsequent steps, we will detail how to utilize **ballots cast**
as a crucial factor in creating a **composite measure of size** for
sampling U.S. election polls. Rather than relying solely on population
size, we will adjust the sample allocation based on historical voter
turnout, ensuring that regions with higher engagement are more
prominently represented in our polling data.

@@

After determining the sample size for each region, we will use
stratified sampling across key demographic categories, such as age,
gender, race/ethnicity, and education level. This method ensures that
our final sample proportionally represents each subgroup within every
region, accurately reflecting the diversity of the U.S. voting
population. To achieve this, the sample will be stratified according to
critical demographic and geographic variables, with strata information
sourced from U.S. Census data available through IPUMS USA
[@ruggles2024ipums].

@@

Once individual weights are calculated for each panel, we will integrate
them into a single weighting scheme that aligns with the target
population's demographic makeup. These weights will then be applied
during data analysis, allowing underrepresented groups to have an
appropriate influence on the results. Finally, we’ll conduct
post-stratification adjustments to ensure that the combined sample
accurately reflects the U.S. voting population, yielding reliable
insights into voter preferences and behaviors.

@@

The survey is designed to capture essential insights into voting
intentions, candidate favorability, and the issues influencing voter
decisions. It will be concise and straightforward, taking no longer than
15 minutes to complete.

@@

In our survey, several questions are adapted from the Emerson College
Polling data [@emerson]. We apply insights from @survey to minimize
response biases. Common response biases identified in survey design
include moderacy bias, extreme response bias, ordering bias,
acquiescence bias, experimenter demand effect (EDE), and social
desirability bias (SDB). Our survey primarily focuses on strategies to
reduce moderacy bias, extreme response bias, ordering bias, SDB, and
acquiescence bias.

>>>>

---
title: "Forecasting the 2024 U.S. Presidential Election Using a Model-Based Approach"
subtitle: "Kamala Harris expects to win on 47.5%, leads Donald Trump by about 1% in 2024 US election"
author: 
  - Diana Shen
  - Jinyan Wei
  - Jerry Yu
thanks: "Code and data are available at: [https://github.com/DianaShen1224/Forecast-2024-US-election](https://github.com/DianaShen1224/Forecast-2024-US-election)."
date: today
date-format: long
abstract: "This study models the 2024 U.S. Presidential Election by analyzing polling data with adjustments for factors like recency and sample size, simulating an approach that captures up-to-date voter sentiment. Using recent 4 months aggregated poll data, the model identifies shifts in candidate support across key battleground states, providing a nuanced view of evolving preferences as election day approaches. By emphasizing recent, high-quality polls, the analysis improves predictive reliability, offering understanding that could inform campaign strategies and public discourse. These findings highlight the value of weighting and time-sensitive adjustments in forecasting methods, balancing accuracy with responsiveness to the latest trends."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
editor: 
  markdown: 
    wrap: 72
---

@@

Understanding voter sentiment is essential for both political campaigns
and analysts, especially with the upcoming U.S. election on the horizon.
Public opinion is highly dynamic and can change swiftly due to various
influences, including media coverage, campaign tactics, and major
events. This study aims to forecast the percentage of support for Kamala
Harris, offering understanding into the elements that shape voter preferences
as the election nears. By examining data from multiple polling sources,
we intend to pinpoint the key factors influencing support, such as the
poll's end date, the polling organization, geographic location, and the
poll's score.

Research by @GelKin93 underscores that while polls can
exhibit variability over a campaign period, they can provide reliable
predictions when adjusted for temporal changes and fundamental factors.
Additionally, @politic highlight the importance of
timing in polling, showing that data closer to election day tends to
stabilize and therefore becomes more predictive. Our research addresses aspects of the literature that often overlook the detailed complexities of polling data, enriching our understanding of voter behavior within the electoral context.

@@

Our findings demonstrate a notable positive correlation between the end date
and the percentage of support, indicating that as the election
approaches, voter support tends to increase. We also observed
considerable variability in support levels based on the polling
organization and state, with certain pollsters consistently reporting
higher support for Harris. The quality of the polls significantly
affected results, with more reputable polls correlating with higher
levels of support. These results emphasize the necessity of considering
both the timing of polls and the characteristics of different polling
firms when analyzing public opinion.

This research is important because precise predictions of voter support
are necessary for effective campaign strategies. By identifying the main
factors influencing support for Harris, campaign teams can customize
their outreach and messaging to resonate better with voters.
Furthermore, recognizing the differences across various polling
organizations and states can assist in resource allocation and strategic
focus during the campaign. Given that elections can be decided by narrow
margins, having trustworthy understanding into voter preferences can
substantially influence the final outcomes.

The structure of this paper is organized as follows: @sec-data 
provides details on the data sources and variables used in our analysis.
@sec-model explains the modeling approach, including the assumptions
and specifications of our linear regression framework. In
@sec-result, we present our findings, emphasizing the key predictors
of Harris's support. Finally, @sec-discussion explores the
implications of our results and suggests potential directions for future
research. @sec-a provide external data detail, @sec-b provide
model detail, @sec-c provide a investigation for pollster Siena College's
methodology, and  @sec-d provide a idealized methodology for polling the poll.

@@

In this study, we utilized several R packages to enhance our data
manipulation, modeling, and visualization capabilities. The tidyverse
package offered a detailed set of tools for data wrangling and
analysis, improving workflow efficiency [@thereferencecanbewhatever].
The here package aided in managing file paths, allowing for easy access
to our data files [@citehere]. We relied on janitor to perform data
cleaning, as it provides functionalities to identify and rectify quality
issues within the dataset [@citejanitor]. For handling date-related
operations, the lubridate package proved invaluable, simplifying the
manipulation of time variables [@citelubridate]. Arrow supported
efficient data input and output in a performance-oriented format,
essential for managing larger datasets [@citearrow]. We use ggplot2 [@citeggplot2] to visualize the analysis of data. In addition to the core packages, we employed several specialized libraries to facilitate specific analytical tasks. The modelsummary package enabled us to generate clean, interpretable model summaries, streamlining the reporting of regression and other statistical results [@citemodelsummary]. RColorBrewer provided color palettes for visualizations, enhancing clarity and visual appeal in our plots [@citeRColorBrewer]. The future package supported parallel processing, optimizing the runtime of intensive computations, especially beneficial in model training [@citefuture]. Finally,for resampling and bootstrapping techniques, we utilized the boot package, which allowed us to assess model stability and reliability [@citeboot1;@citeboot2]. caret facilitated model training and validation, offering a unified interface for cross-validation and performance metrics [@citecaret]. Our coding practices and file organization were informed by the structure outlined
in @tellingstories.

@@

After gathering the responses, the data is subjected to thorough
cleaning and validation procedures to rectify inconsistencies and handle
any missing information. This step is necessary for ensuring that the
dataset accurately mirrors the electorate's sentiments. Following data
cleaning, polling results are aggregated to smooth out individual poll
biases and mitigate random error. This aggregation process employs
weighting based on poll quality, sample size, recency, and the
historical accuracy of each polling agency, as seen in FiveThirtyEight’s
approach (Silver, 2018; Jackman, 2005). By combining multiple polls, the
aggregation method produces a more reliable picture of public opinion
trends over time.

Each entry in the finalized dataset reflects an individual's viewpoint
at a given moment, enabling a detailed analysis of the factors that
shape public opinion as the election nears. This structured methodology
effectively converts subjective opinions into measurable data, providing
valuable understanding into voter behavior and preferences.

@@

The end date is the final day of data collection for a poll, indicating
when the survey period concluded. This date provides necessary context for
the poll results, as public opinion may change over time in response to
events, campaign actions, or other influencing factors. In our analysis, we only choose the polls with end date after July 21 2024, which Kamala Harris first declared in the election.

@@

Recency is a newly created predictor variable in our dataset, specifically
for use in our model. It is calculated as follows Recency = Election Date - End Date,
where Election Date is set to November 5th. This variable quantifies the time
interval between the poll's end date and the election date as a measure of the poll's
relevance and potential impact on voter behavior. In general, polls conducted closer
to the election date provide a more accurate picture of public opinion. The original
dataset includes only dates, and by mutating this variable, we can more intuitively
interpret the number of days before the election that each data point was collected.
Converting this to discrete data enhances its usefulness in constructing predictive models.
@fig-recency demonstrates a strong focus on recent polling data, with the highest frequency of polls occurring within the first few days and gradually declining as recency increases. Periodic peaks around 30, 60, and 90 days suggest some regularity in polling schedules, though the overall trend emphasizes newer data. This distribution highlights the prioritization of recent polls in the dataset.

@@

@fig-state displays the distribution of polls by state, showing how
frequently polling organizations conducted surveys across various U.S.
states and at the national level. The "National" category has the
highest number of polls, indicating a strong emphasis on capturing
overall U.S. sentiment. Certain states, such as Pennsylvania, Wisconsin,
North Carolina, Arizona, Georgia, and Michigan, also show higher polling
frequencies, likely because these are battleground states with the
potential to influence the election outcome significantly. Toward the
right side of the chart, states with minimal polling activity, including
South Carolina, Iowa, and Washington, appear less frequently, possibly
due to their historically predictable or less competitive nature. This
distribution reflects the strategic focus of polling efforts, with
organizations prioritizing both national sentiment and swing states
where public opinion is more volatile. Overall, the chart illustrates how polling resources are allocated as election day
nears, emphasizing areas that could sway the final result.

@@

@fig-pollstertime shows the trend of percentage support for Kamala
Harris over time, with data points and smoothed trend lines for each
pollster. The graph shows the trend of the percentage of respondents supporting
Harris from August through October. Each color corresponds to a specific polling organization, with
prominent pollsters such as Beacon/Shaw, Ipsos, Siena/NYT, Emerson,
Quinnipiac, and YouGov. The smoothed lines demonstrate subtle trends over
time, with some pollsters like Emerson and Beacon/Shaw showing a slight
upward trend, while others like Siena/NYT display a downward trend.
@fig-pollstertime highlights the variability in poll results across
different organizations, reflecting each pollster's methodology and
sample.

@@

In this analysis, we use predictors that capture both the methodological
quality and structural aspects of each poll. Specifically, we include
variables such as `national_poll`, which reflects national support
trends; `pollster`, which represents differences in methodology and
reliability across polling organizations; and `population`, which
accounts for demographic and regional characteristics associated with
each poll. Our combined weighting approach further integrates factors
like recency and sample size to ensure that more recent, larger-sample
polls have a greater impact on the model's predictions, providing a
balanced and detailed assessment of candidate support.

@@

Our model demonstrates a portrait of a nation deeply divided, with Harris
holding a narrow 49% edge over Trump’s 47% in national support. However,
as recent elections have shown, the national popular vote does not
always translate into an Electoral College victory. The U.S. electoral
system, which awards each state’s electoral votes to the candidate with
the majority of votes in that state, means that winning the popular vote
nationally might still leave Harris short of the presidency. This
structural quirk played a defining role in the 2016 election, where
Hillary Clinton’s popular vote win failed to deliver the electoral
majority, paving Trump’s path to the White House. Our findings
underscore this enduring tension: while Harris may have a slight
national advantage, the true battle will be fought state by state, in a
handful of battlegrounds that could flip the election either way.

In states like Nevada and North Carolina, our model highlights just how
close the race remains. North Carolina, for instance, shows both candidates
locked in a near tie around 47% support—a statistical dead heat that
brings the state’s significance into sharp relief. Neveda, meanwhile,
leans modestly toward Trump, a reflection of the unique demographic and
political nuances shaping each battleground. These state-level results
illuminate a significant truth: while national polls offer a snapshot of
overall sentiment, they risk obscuring the specific, local dynamics that
will ultimately decide the outcome. The stakes are high; these are the
states that could swing, the margins that will be watched closely on
election night, as even slight changes in turnout or last-minute shifts
in opinion could tip the balance. improve the number based on the graph results

Ultimately, these findings highlight the complex dance between popular
sentiment and the electoral mechanics of American democracy—a system where
every vote counts, but some states matter just a bit more than others.

@@

In our analysis and shown result, we find out that the use of a weighted model helps to reduce volatility in predicted support trends by assigning greater importance to polls that are both recent and based on larger sample sizes. This approach effectively smooths out abrupt fluctuations that might otherwise result from older or smaller polls, providing a more stable and coherent view of voter sentiment. hough our data filtered with recent polls after Harris's candidacy announcement, voter sentiment remains fluid, with ongoing debates and events likely to influence preferences. By emphasizing recent polls, the model is more responsive to the latest shifts in public opinion, which is especially relevant as election day approaches and voters’ preferences may crystallize. Larger-sample polls, often conducted by established pollsters like Siena/NYT or Emerson, are assumed to be more reliable, and their increased weight in the model further reduces the likelihood of erratic changes driven by smaller, less consistent polls. This decreased volatility allows the model to present a clearer picture of the general support trend for each candidate, reducing noise and highlighting true shifts in sentiment. However, this smoothing effect may also mask some of the localized or short-term dynamics captured by less frequent or smaller-sample polls, which could provide unique understanding into specific voter groups or state-level shifts.

@@

Despite the strengths of our model, limitations remain. Our weighting system prioritizes recent data to reflect current voter sentiment; however, it may miss abrupt shifts triggered by campaign events or changing public opinion. While our model can capture trends, it may not fully anticipate unpredictable electoral dynamics. Additionally, our dataset lacks demographic breakdowns by age, gender, income, and education, which are essential for understanding the preferences of specific voter groups. This absence may obscure meaningful trends within key demographic segments, affecting the model’s precision in reflecting voter sentiment shifts across diverse populations.

@@

To enhance the predictive power of the model, historical voting data, economic
indicators and major news events can be used as background variables. By analyzing
the impact of similar factors on voter sentiment in past elections, we can understand the patterns and trends that may apply to the current campaign. For
example, high-profile events have historically influenced voter opinion, and
understanding these influences can provide a more complete picture of the factors
that drive support for each candidate. Given the underlying conditions that influence
voter preferences over time, this additional context would allow the model to make
more informed predictions.

Another possible improvement is the addition of detailed demographic information, such as age,
gender, income level, and educational background, which would allow us to identify trends among
specific groups of voters and thus greatly enhance our analysis. Different demographics often
have unique responses to campaign issues and activities; for example, younger voters may
prioritize different issues compared to older voters, and income level and educational
attainment may influence political preferences in complex ways. By incorporating this level
of granularity, future analyses can provide deeper understanding into voter behavior and help
develop more targeted campaign strategies.

@@

The cleaned datasets for both candidates are then saved as Parquet files
for efficient storage and access in further modeling and analysis. This
structured approach ensures that the data is accurate, complete, and
optimized for the following statistical analysis.

@@

In this section, we examine the main components of Siena's polling
methodology, including the target population, sampling frame,
recruitment processes, and sampling strategies. Additionally, we discuss
how Siena addresses non-response and review the strengths and weaknesses
of its questionnaire design. By detailing these elements, this appendix
clarifies how Siena College ensures the reliability and validity of its
polling results, offering valuable understanding into voter behavior and
election dynamics.

@@

Siena College Polling Institute is a prominent pollster known for its
detailed and methodologically rigorous surveys. It specializes in
political polling and is particularly recognized for its work in
understanding voter sentiment during elections. Established in 1980 at
Siena College in New York's Capital District, the institute carries out
both expert and public opinion polls. [@aboutsiena].

@@

The sampling frame is a detailed list of registered voters, which
includes demographic information for each voter. This enables the
pollsters to ensure an appropriate representation of voters across
various parties, races, and regions [@poll].

@@

Siena use phone poll to recruit sample. Telephone polling is a way to
gather public opinion by contacting individuals via landlines and mobile
phones, using live interviewers to improve data quality and capture
subtle responses. Through random digit dialing or voter registration
databases, researchers achieve a representative sample across
demographics.

@@

Stratified sampling enhances sample representativeness by ensuring that
smaller subgroups are adequately included, allowing researchers to
allocate resources more efficiently and gain deeper understanding into
specific groups. However, this method can lead to **higher costs** due
to the extensive data collection and analysis needed, especially when
sampling large regions. Stratified sampling also introduces **complexity
in data analysis**, requiring advanced techniques to accurately
interpret subgroup data and appropriate weighting for each stratum.
Additionally, poorly defined strata or imbalanced sampling can lead to
sampling bias. While stratified sampling provides strong representation
and analytical depth, it also brings challenges related to cost,
complexity, and potential bias if not executed with care.

@@

-   Social desirability bias typically stems from the desire of
    respondents to avoid embarrassment and project a favorable image to
    others, resulting in respondents not demonstrateing their actual
    attitudes. The prevalence of this bias will depend on the topic,
    questions, respondent, mode of the survey, and the social context.
    For instance, in some circles, anti-immigrant views are not
    tolerated, and those who hold them may try to hide them. In other
    settings, people express such views more freely.

@@

The questionnaire is concise and straightforward, reducing respondent
fatigue and enhancing clarity, which is necessary for maintaining
engagement. By incorporating both closed- and open-ended questions, it
allows for both quantifiable data and rich qualitative results. Clear
response categories help reduce moderacy bias, encouraging participants
to choose decisively rather than defaulting to neutral answers.
Additionally, varied question types help mitigate acquiescence bias by
encouraging honest responses and avoiding leading language.

@@

This appendix details the methodology and design for conducting a U.S.
presidential election forecast survey with a budget of $\$100,000$. The
objective is to generate an accurate and reliable prediction of the
election outcome while ensuring data quality through careful
sampling, recruitment, validation, and aggregation of results.\

@@

In the subsequent steps, we will detail how to utilize **ballots cast**
as a necessary factor in creating a **composite measure of size** for
sampling U.S. election polls. Rather than relying solely on population
size, we will adjust the sample allocation based on historical voter
turnout, ensuring that regions with higher engagement are more
prominently represented in our polling data.

@@

After determining the sample size for each region, we will use
stratified sampling across key demographic categories, such as age,
gender, race/ethnicity, and education level. This method ensures that
our final sample proportionally represents each subgroup within every
region, accurately reflecting the diversity of the U.S. voting
population. To achieve this, the sample will be stratified according to
significant demographic and geographic variables, with strata information
sourced from U.S. Census data available through IPUMS USA
[@ruggles2024ipums].

@@

Once individual weights are calculated for each panel, we will integrate
them into a single weighting scheme that aligns with the target
population's demographic makeup. These weights will then be applied
during data analysis, allowing underrepresented groups to have an
appropriate influence on the results. Finally, we’ll conduct
post-stratification adjustments to ensure that the combined sample
accurately reflects the U.S. voting population, yielding reliable
understanding into voter preferences and behaviors.

@@

The survey is designed to capture essential understanding into voting
intentions, candidate favorability, and the issues influencing voter
decisions. It will be concise and straightforward, taking no longer than
15 minutes to complete.

@@

In our survey, several questions are adapted from the Emerson College
Polling data [@emerson]. We draw on recommendations from @survey to minimize
response biases. Common response biases identified in survey design
include moderacy bias, extreme response bias, ordering bias,
acquiescence bias, experimenter demand effect (EDE), and social
desirability bias (SDB). Our survey primarily focuses on strategies to
reduce moderacy bias, extreme response bias, ordering bias, SDB, and
acquiescence bias.
